\section{Introduction}
\label{sec:introduction}
Container loading represents a critical activity in logistics operations that directly influences transportation efficiency and operational costs. The global container shortage that intensified since 2021 due to the COVID-19 pandemic, coupled with disruptions such as the 2024 Red Sea shipping crisis that caused freight rate increases up to 173\% for Asia-Europe routes, has further emphasized the importance of optimal space utilization \cite{Hoa2024}. Optimal loading maximizes space utilization, reduces trip frequency, and lowers operational expenses and carbon emissions \cite{Tresca2022}. However, loading operations for heterogeneous items remain predominantly manual \cite{Ananno2024}. Case studies in chemical manufacturing industries reveal that shipping managers often plan routes and loading arrangements based solely on personal experience due to the absence of decision support tools, resulting in inefficient distance traveled and increased vehicle costs \cite{Jomthong2024}. This manual approach has several fundamental limitations: it requires specialized training with associated ramp-up periods, produces efficiency highly dependent on individual operator capabilities, and cannot guarantee consistent load stability—a safety concern particularly in non-walled open containers such as pallets \cite{Ananno2024}.
\par
The container loading problem is formally known as the Three-Dimensional Bin Packing Problem (3D-BPP), an optimization challenge of placing a set of items into containers with the objective of minimizing empty space or the number of required containers. 3D-BPP is classified as NP-hard, meaning computational complexity increases exponentially as problem size grows \cite{Ma2025}. Complexity escalates further when considering practical constraints such as maximum weight limits, load stability, item orientation restrictions, load-bearing capacity of individual items \cite{Krebs2023}, and product category compatibility where certain items cannot be packed together \cite{Tsao2024}. The problem becomes particularly challenging when items consist of numerous types with highly variable dimensions, as commonly encountered in e-commerce logistics, courier service operations \cite{Ma2025}, and the textile and garment industry where products vary in designs, sizes, and colors \cite{Hoa2024}.
\par
Various approaches have been developed to solve 3D-BPP. Classical methods include heuristic algorithms such as First Fit Decreasing and Best Fit, which place items sequentially according to predetermined rules \cite{Silva2016}. Layer-building methods construct horizontal layers then stack them vertically, with recent matheuristic approaches combining mixed integer linear programming (MILP) formulations achieving pallet configurations in under 30 seconds per bin on average \cite{Tresca2022}. Block-building heuristics aggregate items into larger blocks to reduce problem complexity before applying placement strategies \cite{Ananno2024}. Wall-building algorithms decompose the 3D problem into sub-problems by composing items into vertical walls then stacking these walls into bins \cite{Hoa2024}. Recent work has also addressed irregular-shaped and deformable items, where shape-changing factors during compression can enhance loading efficiency \cite{Zuo2022}. Despite these algorithmic advances, Tresca et al. \cite{Tresca2022} noted that commercial warehouse management systems still lack effective algorithms to automate optimal pallet configuration, a finding corroborated by comparative analyses showing significant performance gaps between commercial container loading software and state-of-the-art optimization algorithms \cite{Mihu2024}.
\par
Recent developments demonstrate the application of metaheuristics and artificial intelligence for 3D-BPP. Khairuddin et al. \cite{Khairuddin2020} developed a Genetic Algorithm (GA)-based simulator that visualizes the optimization process through adaptive chromosome length representation. Ma et al. \cite{Ma2025} combined block-building heuristics, GA, and simulated annealing to handle strongly heterogeneous items while satisfying six practical constraints. Ananno and Ribeiro \cite{Ananno2024} proposed a two-stage algorithm incorporating constructive heuristics for layer generation followed by GA for leftover items, tested with real industrial data achieving full palletization across diverse orders while respecting eight practical constraints including stability with 75\% minimum support area. Hoa et al. \cite{Hoa2024} applied GA combined with wall-building algorithms for the textile industry, achieving container fill rates up to 91.67\% while respecting purchase order priorities; earlier work by Sheng et al. using simulated annealing achieved approximately 85\% fill rates with deadline-based prioritization \cite{Hoa2024}. From the artificial intelligence perspective, Deep Reinforcement Learning (DRL) has begun to be applied to 3D-BPP. Zhao et al. \cite{Zhao2022} employed DRL with stacking trees for stability analysis, reducing computational complexity from $O(N^2)$ to $O(N \log N)$ while achieving 99.9\% stability analysis accuracy and approximately 10\% improvement in space utilization over previous DRL approaches. Shuai et al. \cite{Shuai2023} developed compliant-based robotic bin packing systems that handle unavoidable uncertainties from sensors and planners through compliant end-effectors and accompanying motion strategies. Murdivien and Um \cite{Murdivien2023} used game engines for DRL training simulation, enabling more intuitive visualization of learning processes. Hybrid heuristic-DRL approaches integrating extreme point sorting with Proximal Policy Optimization have also shown promising results \cite{Wong2024}. Zhang et al. \cite{Zhang2024} proposed a combination of Generative Adversarial Networks with GA to improve solution quality. For real-world air cargo applications, He{\ss}ler et al. \cite{Heler2025} developed a fast insertion heuristic embedded in Randomized Greedy Search, introducing extended extreme point concepts for handling non-cuboid unit load devices.
\par
Visualization plays an important role in bin packing solutions as it enables result validation and provides guidance to operators. Krebs and Ehmke \cite{Krebs2023} developed open-source tools for solution validation and visualization, providing vehicle routing and loading views with feasibility checking capabilities. Their work highlighted a transparency issue in the literature: published results often report only objective function values without detailed placement coordinates, making solution verification difficult and sometimes revealing infeasible or incorrectly reported solutions \cite{Krebs2023}. However, these tools are desktop-based (implemented in C++ and Java) and primarily targeted at researchers for algorithm validation rather than operational field guidance. Poerwandono and Fiddin \cite{Poerwandono2023} implemented web-based 3D visualization using Three.js for container loading with Tabu Search algorithm, demonstrating the feasibility of browser-based rendering but without integrated step-by-step loading guidance for operators. Beyond interface limitations, another significant challenge is that algorithm testing often relies on random datasets that inadequately reflect real-world logistics scenarios \cite{Ribeiro2023}. Transportation Management Systems (TMS) have emerged as pivotal tools for logistics optimization \cite{Ranjangaonkar2024}, yet integration between algorithmic optimization and practical operator guidance remains limited. A gap exists for web-based systems that integrate bin packing algorithms with interactive 3D visualization capable of handling realistic data scenarios and providing step-by-step loading guidance accessible to warehouse operators without specialized software installation.
\par
This research develops a web-based container loading planning system to bridge this gap. Unlike existing desktop-based tools that target researchers \cite{Krebs2023} or standalone visualization implementations \cite{Poerwandono2023}, this system provides an integrated solution accessible through standard web browsers without specialized software installation. The system uses a 3D bin packing library with built-in stability checking and gravity simulation features, integrating it through a layered architecture that separates the computation engine from the data management backend. Interactive 3D visualization using WebGL-based rendering displays algorithmic calculation results and provides step-by-step loading guidance, enabling operators to visualize the item placement sequence chronologically. This approach addresses the operational gap identified in the literature where algorithmic solutions lack practical guidance for warehouse staff \cite{Tresca2022, Ananno2024}.
\par
This research has three primary objectives. First, to design and implement a layered system architecture that effectively integrates a 3D bin packing library with web-based visualization for practical logistics operations. Second, to develop interactive 3D visualization with step-by-step playback that provides actionable loading guidance to operators, bridging the gap between algorithmic optimization and physical execution. Third, to evaluate system effectiveness using realistic heterogeneous item scenarios to validate practical applicability, measuring achieved space utilization, computation time scalability, and the impact of algorithm configuration on loading performance.
